### 2023-05-31 test_running_updating.Rmd
updated tests following API update

```{r}
library(httptest) # installed from https://github.com/nealrichardson/httptest/commit/5fc2be9f8627fa36d04ee06de0291c1d7633d1a8
library(testthat)
library(roxygen2)
library(devtools)
system("rm -rf tests/api")
roxygen2::roxygenise()
devtools::install(build_vignettes = FALSE)
testthat::test_local(".")
```

>>>>

```{r}
library(httptest)
library(testthat)
library(roxygen2)
library(devtools)
system("rm -rf tests/api")
roxygen2::roxygenise()
devtools::install(build_vignettes = FALSE)
testthat::test_local(".")
```
